---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

<!-- badges: start -->
<!-- badges: end -->

# fpurrr

A package / module, only be accessed by `box::use()`, is a restructured version of `{purrr}` in a complete modular version. Take note that this is not an R package, it is still a package but on complete different world, similar to Python packages. 

## Installation

`{fpurrr}` is only accessible via `carrier` installation.

Install `carrier` first (see the [guide](https://github.com/joshuamarie/carrier#installation)). Then install the package via terminal: 

``` bash
carrier install gh:joshuamarie/fpurrr
```

You must install `{box}` through

``` r
# install.packages(pak)
pak::pak("joshuamarie/box@carrier-module-support")
```

Since the patches are applied on only on this forked version found on `carrier-module-support` branch. 

## Usage

`{fpurrr}` is still `{purrr}` but with actual true and hierarchical structure of a package. Let's take an example:

```{r}
box::use(
    fp = fpurrr, 
    fpurrr/map,
)
```

`fp` is an aliased `{fpurrr}` module, which carries the whole imports without attaching the names, so everything are found inside. Since `fpurrr/map` was also imported directly, the `map` submodule is available on its own, without going through the `fp` alias. 

### Examples

Note: Both paths reach the same underlying code, so `fp$map` and `map` are interchangeable:

```{r}
# Without types
fp$map$call(1:5, sqrt)
map$call(1:5, sqrt)

# With types
fp$map$call@dbl(1:5, sqrt)
map$call@dbl(1:5, sqrt)
```

## Dependencies

`{fpurrr}` relies on:

- [`{rlang}`](https://rlang.r-lib.org/)
- [`{purrr}`](https://purrr.tidyverse.org/)
- [`{S7}`](https://rconsortium.github.io/S7/)

These install automatically the first time you run `carrier install --install-deps gh:joshuamarie/fpurrr`.
